Datasheet for OpenDataToronto's Fire Incidents

### 2024-04-16 other/datasheet/datasheet_fire_incidents.qmd
update README and datasheet reference list

---
title: "Datasheet for OpenDataToronto's Fire Incidents"
author: 
  - Jimmy Luc
thanks: "Code and data are available at: [https://github.com/rex009x/fire-incidents-toronto](https://github.com/rex009x/fire-incidents-toronto)"
date: today
date-format: long
format: pdf
number-sections: true
---

Extract of the questions from Gebru et al. (2021).

>>>>

---
title: "Datasheet for OpenDataToronto's Fire Incidents"
author: 
  - Jimmy Luc
thanks: "Code and data are available at: [https://github.com/rex009x/fire-incidents-toronto](https://github.com/rex009x/fire-incidents-toronto)"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.
